%%%%%%%%%%
% RESUME %
%%%%%%%%%%
\thispagestyle{empty} 

\resizebox{!}{0.05mm}{.}

\vspace{-2cm}

\paragraph{Abstract}
\ \vspace{1.4ex}
\\
\indent
A reversible quantum memory allowing us to store and retrieve quantum information serves as a key necessity for implementing many of novel quantum information protocols. As light serves as a reliable long-range carrier of quantum information, and atoms offer the possibility of long storage times, current attempts at creating quantum memories focus on the transfer of the quantum fluctuations of light onto atomic coherences.  The work in this thesis focuses on the development of a quantum memory for squeezed light using an ensemble of cold Cesium atoms stored in a magneto-optical trap.  Our two major milestones were the development of a source of nonclassical light, and the development of a suitable atomic medium for storage.

We first present the results of our efforts to generate a source of squeezed vacuum states resonant with the Cesium $D_2$ line using a PPKTP nonlinear crystal inside of an optical parametric oscillator.  Additionally, we characterize these squeezed states by carrying out a quantum state tomography using an iterative maximum likelihood approach.

Next we look at the development of a new experiment which would allow us to use cold Cesium atoms as a storage medium in our recently developed magneto-optical trap. As this requires an array of novel tools and experimental techniques, we will discuss the development of these elements, and how they have furthered our progress towards storing quantum states onto our Cesium atoms, and eventually entangling two atomic ensembles.



\vspace{0.5cm}

\noindent{\bf Keywords:} quantum optics, quantum information, continuous variables, quantum memory, optical parametric oscillator, squeezed states, entanglement, quantum tomography, electromagnetically induced transparency, cesium vapor.



\vspace{5mm}
\newpage
\thispagestyle{empty}
\newpage
\null
\cleardoublepage
\thispagestyle{empty}
\paragraph{Résumé}
\ \vspace{1.4ex}
\\
\indent
Une mémoire quantique réversible permettant de stocker et relire de
l'information quantique est une composante majeure dans la mise en oeuvre de
nombreux protocoles d'information quantique.  Comme la lumière est un porteur de
l'information quantique fiable sur des longues distances, et comme les atomes
offrent la possibilité d'obtenir de longues durées de stockage, le recherche
actuelle sur la création d'une mémoire quantique se concentre sur la transfert
des fluctuations quantiques de la lumière sur des cohérences atomiques.  Le
travail réalisé durant cette thèse porte sur le développement d'une mémoire
quantique pour la lumière comprimée, utilisant un ensemble d'atomes froids de
Césium stockés dans un piège magnéto-optique.  Nos deux principaux objectifs
étaient le développement d'une source de lumière non-classique, et le développement d'un millieu atomique pour le stockage de celle-ci.


Tout d'abord, nous commençons par présenter la construction d'un oscillateur
paramétrique optique qui utilise un cristal nonlineaire de PPKTP.  Cet OPO
fonctionne comme source d'états de vide comprimé résonant avec la raie $D_2$ du Cesium.  Nous caractérisons ces états grâce à une reconstruction par tomographie quantique, en utilisant une approche de vraisemblance maximale.

Ensuite, nous examinons une nouvelle expérience qui nous permet d'utiliser comme
millieu de stockage des atomes froids de Césium dans un piège magneto-optique
récemment développé.  Car cette expérience exige l'utilisation de nouveaux
outils et techniques, nous discutons le développement de ceux-ci, et comment ils
ont contribué à notre progression vers le stockage des états quantiques dans nos
atomes des Césium, et finalement vers l'intrication de deux ensembles atomiques.

\vspace{0.5cm}

\noindent{\bf Mots clés:} optique quantique, information quantique, variables continues, mémoire quantique, transparence induite électromagnétiquement, vapeur de césium, oscillateur paramétrique optique, états comprimés, intrication, tomographie quantique.

\newpage
\thispagestyle{empty}
